Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-03-16 manuscript.tex
Updated some parts of the SN intro
added updated manuscript.tex

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{The Skew Normal distribution} \label{sec:2}
\jessi{This section is too complicated.  I suggest we define the skew normal in terms of the parameters that are used later, then relegate additional details, including the optimization, to an appendix section.}
\comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
18) Paragraph 4: "By using the so-called direct parameterization (DP) defined in Eq. 2 problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha$ = 0, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates."
A poorly constructed sentence that simply confuses me! The authors are trying to say too many things in one sentence which loses the reader.
19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}

The Skew Normal (SN) distribution, introduced by \cite{Azzalini1985}
\jessi{Wikipedia says this was introduced in O'Hagan and Leonard (1976), Bayes estimation subject to uncertainty about parameter constraints.  However, it seems this may just be a 2-parameter class. I don't know that we need to get into the history anyway, we can just discuss the SN and reference the Azzalini paper.}
, is a class of probability distributions which includes the Normal distribution as a special case. The SN distribution has, in addition to a position and a scale parameter, a third parameter which describes the asymmetry of the distribution.

Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
\begin{equation} \label{def:snd}
SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN. It is possible to provide a general expression where both the location and the scale parameters are included. If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:

\begin{equation} \label{def:snd_gen}
SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
\end{equation}
and $Y \sim SN(\xi, \omega^{2}, \alpha)$.

@@

\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_normal_densities.pdf} 
   \caption{Density function of a $SN(\alpha)$ for different choices of $\alpha$. For negative values of $\alpha$ the asymmetry will be on the left tail of the distribution.}
   \label{fig:SN.plot}
\end{figure}

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{The Skew Normal distribution} \label{sec:2}
\jessi{This section is too complicated.  I suggest we define the skew normal in terms of the parameters that are used later, then relegate additional details, including the optimization, to an appendix section.}
\comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
18) Paragraph 4: "By using the so-called direct parameterization (DP) defined in Eq. 2 problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha$ = 0, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates."
A poorly constructed sentence that simply confuses me! The authors are trying to say too many things in one sentence which loses the reader.
19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}
\jessi{Wikipedia says this was introduced in O'Hagan and Leonard (1976), Bayes estimation subject to uncertainty about parameter constraints.  However, it seems this may just be a 2-parameter class. I don't know that we need to get into the history anyway, we can just discuss the SN and reference the Azzalini paper.}

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \cite{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter, a third parameter which describes the asymmetry, or the skewness, of the distribution.

Considering a random variable $Y\in \mathbb R$ which follows a skew normal distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density can be written as 
\begin{equation} \label{def:snd_gen}
SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard normal distribution is a Gaussian distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters are displayed in Figure \ref{fig:SN.plot}.

%Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
%\begin{equation} \label{def:snd}
%SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
%\end{equation}
%where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN. It is possible to provide a general expression where both the location and the scale parameters are included. If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:
%\begin{equation} \label{def:snd_gen}
%SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
%\end{equation}
%and $Y \sim SN(\xi, \omega^{2}, \alpha)$.

@@

\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
   \caption{Density function of a $SN(\alpha)$ for different choices of $\alpha$. For negative values of $\alpha$ the asymmetry will be on the left tail of the distribution.}
   \label{fig:SN.plot}
\end{figure}
